---
title: "EV Sentiment Analysis SURV 727"
author: "Sagnik Chakravarty and Namit Shrivastava"
subtitle: "University of Maryland, College Park"
format: 
  pdf:
    latex-engine: xelatex
toc: True
lot: TRUE
lof: TRUE
editor: visual
---

\newpage

The initial task is to gather all the possible sources of data from the internet regarding EV

# Reddit

```{r}
# install.packages("RedditExtractoR")
# install.packages("tidytext")
```

```{r warning=FALSE, message=FALSE, include=FALSE}
library(RedditExtractoR)
library(tidytext)
library(dplyr)
library(pander)
library(knitr)
library(ggplot2)
library(gridExtra)
library(scales)
library(topicmodels)
library(stringr)
library(quanteda)
library(kableExtra)
```

## Collecting Reddit Data

```{r}
ev_reddit <- find_subreddits("Electric Vehicle")
ev_df_reddit <- data.frame(ev_reddit)
ev_df_reddit_clean <- ev_df_reddit %>%
  select(subreddit, 
         title, 
         description, 
         subscribers, 
         date_utc)

ev_df_reddit_clean$date_utc <- as.Date(ev_df_reddit_clean$date_utc)
rownames(ev_df_reddit_clean) <- 1:nrow(ev_df_reddit_clean)
str(head(ev_df_reddit_clean, 1))
pander(dim(ev_df_reddit))
pander(dim(ev_df_reddit_clean))
```

```{r fig.cap="Subscriber count by Subreddits", fig.width= 5}
ev_df_reddit_clean %>% ggplot(aes(x = subreddit, y = subscribers))+
  geom_bar(stat = 'identity',
           color = 'black',
           fill = 'red')+
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 0,
                                   hjust = 1,
                                   size = 2))+
  scale_y_continuous(
    breaks = pretty_breaks(n=5))

```

Now as we can see there are 138 subreddits were we were able to find the keyword = 'Electric Vehicle'. Now working with so many subreddits is not feasible hence we would be narrowing it down to top 5 subreddits. First we would exclude the subreddit based on there descriptions then we would select the top 5 sub reddits

```{r message=FALSE}
desc_clean <- function(x){
  tk <- tibble(line = 1, text = x)
  tk <- tk %>% 
    unnest_tokens(word, text) %>% 
    anti_join(stop_words)
  return(tolower(str_c(tk$word, collapse = ' ')))
}

ev_df_reddit_clean <- ev_df_reddit_clean %>%
  rowwise() %>%
  mutate(cleaned_description = desc_clean(description)) %>%
  select(-description) %>%
  ungroup()
```

```{r}
check_ev <- function(x){
  keywords <- c('electric car',
                'electric vehicle',
                'ev',
                'motor',
                'car',
                'battery',
                'autonomous',
                'tesla'
                )
  pattern <- paste0("\\b(", paste(keywords, collapse = "|"), ")\\b")
  any(str_detect(x, pattern = pattern))
}

ev_df_reddit_clean <- ev_df_reddit_clean %>% 
  rowwise()  %>%
  mutate(ev_related = if_else(check_ev(cleaned_description), TRUE, FALSE)) %>%
  ungroup()
```

```{r fig.cap= 'Subreddit to be used for the study'}
reddit_df <- ev_df_reddit_clean %>%
  filter(ev_related == TRUE) %>%
  arrange(desc(subscribers))  %>% 
  head(n=5)
reddit_df[c(-5,-6)] %>%
  pander(caption = "Subreddits Related to EV")


reddit_df %>% ggplot(aes(x = subscribers,
                         y = subreddit))+
  geom_bar(stat = 'identity',
           fill = 'black')+
  theme_classic()
```

so the subreddits we would be looking at are

r/teslamotors, r/fuckcars, r/Rivian, r/TeslaModel3, r/electricvehicles

```{r}
write.csv(reddit_df, 'workable_reddit_df.csv')
```
